Building a framework to perform automated verification of solar photovoltaic off-grid systems

### 2018-10-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
reviewed abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%Alessandro input: makecell package to permite line break inside tables
\usepackage{makecell}

@@

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A}{ccording} to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide. 
%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) are now becoming a mainstream electricity provider.
% changing the way the world is powered. 
Based in data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
%The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
%(low greenhouse gases emissions)
%operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. 
%Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
% 
%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.

%Apart from PV modules; the 
%PV systems consist of PV modules, battery bank, controller, and inverter, plus the load. %Moreover, the optimum sizing of these devices is important for reliable operation.
%Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}. %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application. 
In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market.

@@

Desiging any complex system, as a PV, more time is spent on verification than on construction, as shown in \cite{Baier}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects. 
%with behavior that is, in principle, well determined. 
 This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification.%, as defined by \cite{Trindade}.

This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system.

@@

@@

The remainder of this paper is organized as follows: Section II gives the background. Section III describes the design and validation of PV system. Section IV describes the mathematical modeling. Section V presents the automated verification. The methodology is presented at section VI. Section VII is devoted to the results, and section VIII to the related work. Section IX presents the conclusion and describes future work.

>>>>

%Alessandro input: makecell package to permite line break inside tables
\usepackage{makecell}
\usepackage{xcolor}

@@

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A}{ccording} to Coelho et al. \cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) are now becoming a mainstream electricity provider.
% changing the way the world is powered. 
Based on data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
%The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
%(low greenhouse gases emissions)
%operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. 
%Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
% 
%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy. 
%
%Apart from PV modules; the 
%PV systems consist of PV modules, battery bank, controller, and inverter, plus the load. %Moreover, the optimum sizing of these devices is important for reliable operation.
%Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}. %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application. 
In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market \textcolor{red}{cite here those tools}.

@@

Desiging any complex system, as a PV, more time is spent on verification than on construction, as described by Baier and Katoen\cite{Baier}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects. 
%with behavior that is, in principle, well determined. 
 This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification.%, as defined by \cite{Trindade}. 
%
This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system.

@@

\textcolor{red}{This introduction is missing the description of the vision, approach and results. In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}

@@

 %This paragraph is useless.
%The remainder of this paper is organized as follows: Section II gives the background. Section III describes the design and validation of PV system. Section IV describes the mathematical modeling. Section V presents the automated verification. The methodology is presented at section VI. Section VII is devoted to the results, and section VIII to the related work. Section IX presents the conclusion and describes future work.
